Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-22 constantRate/ConstCompFuzzExt-reorg.tex
handled reusability in the intro

\paragraph{Fuzzy Extractors}
Cryptography relies on long-term secrets for key derivation and authentication. However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
and quantum information~\cite{bennett1988privacy}). Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and non-interactive versions.  In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
 A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.

@@

%Prime candidate sources for authentication have $\Huse\le 0$.  
Unfortunately, prime candidate sources for authentication have more errors than entropy. 
For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}. Physical unclonable problems with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.

@@

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.  Table~\ref{tab:upper bounds} summarizes our constructions.

@@

We switch to computational security to obtain constructions with additional features. Boyen showed information-theoretic reusability fuzzy extractors incur entropy loss proportional to the number of corrected error patterns~\cite[Theorem 11]{Boyen2004}.  For sources with more errors than entropy, information-theoretic reusability is impossible~(see \secref{sec:reusable} for discussion).

Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy. It provides reusability against \emph{computational} adversaries. 
The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution. 
 This construction, however, requires that the fraction of errors is subconstant. \bnote{reasonable?}

Our third construction removes the need for fresh entropy in the symbols. 
It is secure when symbols in $w$
each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).  This construction can correct a constant fraction of errors.  However, this construction requires a large alphabet size~(super-polynomial in the security parameter).

%\bnote{rewrite this!}
%Our first construction is secure when symbols in $w$ each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover, a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).  This construction can correct a constant fraction of errors~($\Theta(\ell)$).  However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
%
%We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.  Our second construction supports an arbitrary alphabet size~(though it only achieves $\Huse\le 0$ when the alphabet size is super-constant).  However, these improvements come at a price to error-tolerance: it tolerates a sub-constant fraction of errors~($o(\ell)$).  
%
%\consref{cons:sampling} comes with an additional feature: reusability.  Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.  The enrolled values $w_i$ and $w_j$ are not assumed to be equal, and so information leakage may add up.  Indeed, Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.  Our second construction allows for arbitrary correlation between $w_i$ and $w_j$ against computational adversaries\footnote{Our restriction to computational adversaries implies that the adversary only sees a polynomially bounded number of reuses.  It remains an open problem to construct a polynomially reusable fuzzy extractor against unbounded adversaries.} as long as each marginal $W_i$ is an admissible distribution.  %We do not considering the joint distribution $W_1,..., W_q$.

\begin{table}
\begin{tabular}{l | l | l | l }
Construction & Security & Features & Limitations \\
\hline
\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
&&structure & fresh entropy \\\hline
\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
&& & error tolerance\\\hline
\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
& &  symbols & size symbols
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
\label{tab:upper bounds}
\end{table}

>>>>

\paragraph{Fuzzy Extractors}
Cryptography relies on long-term secrets for key derivation and authentication. However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
and quantum information~\cite{bennett1988privacy}). Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and non-interactive versions.  In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
 A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.

@@

%Prime candidate sources for authentication have $\Huse\le 0$.  
Unfortunately, sources that have been proposed as prime candidates for authentication have more errors than entropy. 
For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}. PUFs with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.

@@

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.  Table~\ref{tab:upper bounds} summarizes our constructions. \lnote{Note sure about the first line of this table. What does ``exploit distribution structure'' mean? Also, can we make it look a bit better? Perhaps center. Perhaps also remove some lines. Perhaps make "main feature" column the same part of speech in each entry.}

@@

We switch to computational security to obtain constructions with additional features. Our second construction provides reusability (against computationally bounded adversaries).  Like the first construction,
it requires that a constant fraction of symbols contribute fresh entropy. However,
the reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution. The switch to computational security is necessary here: as discussed in \secref{sec:reusable}, it is impossible to obtain such reusability information-theoretically for sources with more errors than entropy.  
This construction requires that the fraction of errors is subconstant.

Our third construction removes the need for fresh entropy in the symbols and allows a constant fraction of symbols of errors, at the cost of requiring a large alphabet size~(super-polynomial in the security parameter).
It is secure if symbols in $w$
each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
a constant fraction of symbols in $w$ may have little or no entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).  %\bnote{rewrite this!}
%Our first construction is secure when symbols in $w$ each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover, a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).  This construction can correct a constant fraction of errors~($\Theta(\ell)$).  However, this construction requires a large alphabet size~(super-polynomial in the security parameter).
%
%We improve the entropy and alphabet size requirements in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.  Our second construction supports an arbitrary alphabet size~(though it only achieves $\Huse\le 0$ when the alphabet size is super-constant).  However, these improvements come at a price to error-tolerance: it tolerates a sub-constant fraction of errors~($o(\ell)$).  
%
%\consref{cons:sampling} comes with an additional feature: reusability.  Boyen~\cite{Boyen2004} defined reusable fuzzy extractors: multiple readings $w_1,..., w_q$ are enrolled and the adversary sees the corresponding public values $p_1,..., p_q$ and possibly some of the derived keys.  The enrolled values $w_i$ and $w_j$ are not assumed to be equal, and so information leakage may add up.  Indeed, Boyen showed that with an unbounded number of reuses it is only possible to support limited correlations between $w_i$ and $w_j$~\cite[Theorem 11]{Boyen2004}.  Our second construction allows for arbitrary correlation between $w_i$ and $w_j$ against computational adversaries\footnote{Our restriction to computational adversaries implies that the adversary only sees a polynomially bounded number of reuses.  It remains an open problem to construct a polynomially reusable fuzzy extractor against unbounded adversaries.} as long as each marginal $W_i$ is an admissible distribution.  %We do not considering the joint distribution $W_1,..., W_q$.

\begin{table}
\begin{tabular}{l | l | l | l }
Construction & Security & Main Feature & Main Limitation \\
\hline
\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
&&structure & fresh entropy \\\hline
\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
&& & error tolerance\\\hline
\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
& &  symbols & size symbols
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
\label{tab:upper bounds}
\end{table}
